---
title: combine rows in data frame containing NA to make a complete row
author: "Xin \U0001F493 Zhu"
date: '2019-03-02'
slug: combine-rows-containing-NA-data-frame-complete-rows
bibliography:
  - miscellaneous.bib
link-citations: true
categories:
  - programming
tags:
  - R
  - Rmarkdown
  - data-wrangling
images: ~
draft: yes
---

Sometimes we want to combine rows with overlapping information but separated in different rows, which is really annoying for downstream analysis. I couldn't come up with an elegant solution until finding an answer on [stackoverflow](https://stackoverflow.com/a/47563618/10538503)[@combine-row-to-make-complete-row]. To prevent me from struggling to find the answer again, I decide to make a note here. 

Below is the minimal example. 

```{r message=FALSE, warning=FALSE, results="hide"}
library(tidyverse)
```

```{r example-data}
df <- data.frame(A = c(1,1,2,2,2),
                 B = c(NA,2,NA,4,4),
                 C = c(3,NA,NA,5,NA),
                 D = c(NA,2,3,NA,NA),
                 E = c(5,NA,NA,4,4))
df
```

We use `na.omit` and `unique` to create a `coalesce` and then `summerize_all` the data for each column to merge rows. 
```{r make-it-a-complete-row}
df %>% group_by(A) %>% summarise_all(list( ~ na.omit(unique(.))) )
```

Now we're done. 