---
title: fancy ggplot2 axis format
author: Xin 💓 Zhu
date: '2019-03-02'
slug: fancy-ggplot2-axis-format
categories:
  - programming
tags:
  - ggplot2
  - R
  - Rmarkdown
images: ~
draft: no
output:
  blogdown::html_page:
    toc: true
---

## Prerequisite

```{r knitr-options}
knitr::opts_chunk$set(fig.dim = c(8, 8),
                      message = FALSE,
                      warning = FALSE)
```

```{r results="hide"}
library(tidyverse)
```

## Fancy the axis output

We take the `diamonds` dataset from `ggplot2` package as an example. The default `scales::scientific_format()` generates a little ugly axis format that is not nice to human instinct, such as '1.5e+04'.

```{r default-scales-scientific-axis-format}
ggplot(diamonds, aes(color, price)) + 
  geom_point() + 
  facet_grid(cut ~ clarity) + 
  scale_y_continuous(labels = scales::scientific_format())
```

The format '1.5 x 10^4^' is preferable for us, at least for me. To achieve this, we first create a `fancy_axis` function. 

```{r fancy-axis-format}
fancy_axis <- function(x) {
    ifelse(x == 0, "0", parse(text = gsub("[+]", "", gsub("e", " %*% 10^", scales::scientific_format()(x)))))
}
```

Now we just need specify the `scale_y_continuous(labels = fancy_axis)` and get a pretty nicer look. 

```{r nicer-scales-scientific-axis-format}
ggplot(diamonds, aes(color, price)) + 
  geom_point() + 
  facet_grid(cut ~ clarity) + 
  scale_y_continuous(labels = fancy_axis)
```


